Revisiting the Classics: Online RL in the Programmable Data-Plane

### 2020-10-30 paper/paper.tex
Appended notes to motivation.

	\item Training deep RL models has its own costs (need many parallel simulations). What if we only have one stream of experience to learn from? E.g., evolution of the system is too difficult to predict and model. In general, DNNs can't be trained effectively from a single, online, real-time stream of experience.
	\begin{itemize}
		\item What can I do with these observations?
		\begin{itemize}
			\item This suggests that we should also look into non-DNN based RL approaches, if we find that RL is the best tool for the job.
		\end{itemize}
		\item What can I do to address this?
		\begin{itemize}
			\item Employ classical RL methods, which don't need many streams of parallel execution traces to learn effectively.
		\end{itemize}
		\item If addressed, what do I use them for?
		\begin{itemize}
			\item There's ongoing research which attempts to execute NN/DNN-based RL/ML models in switches, but these work under heavy concessions.
			\item Training and format conversion must happen off of the device, so can't be done online.
		\end{itemize}
		\item What applications is this affecting?
		\begin{itemize}
			\item In-network RL applications needing real-time evolution, where DNN online training is not doable.
			\item Likely invites some accuracy impact---linear (e.g., tile-coded) function approximation not as expressive or powerful as DNNs.
		\end{itemize}
		\item What would its solution be useful for?
		\begin{itemize}
			\item Ensures that online learning is possible in the contexts we're interested in.
		\end{itemize}
	\end{itemize}

	\item PDP hardware is advertised as supporting P4, EBPF... But almost all implementations compile to a more complex/expressive language. Presence of externs is almost universal when it comes to in-switch compute---i.e., Tofino Native Architecture\footnote{\url{    https://www.barefootnetworks.com/products/brief-p4-studio/}}, Netronome Micro-C\footnote{\url{https://www.netronome.com/products/datapath-programming-tools/}}, P4$\rightarrow$NetFPGA toolchain\footnote{\url{https://github.com/NetFPGA/P4-NetFPGA-public}}.
	\begin{itemize}
		\item What can I do with these observations?
		\begin{itemize}
			\item We should use P4 where possible to make implementation of in-network compute possible.
			\item \emph{But} we would be remiss not to make use of the multicore, general-purpose compute that the core on many of these devices are fundamentally built to do.
			\item In-network compute and/or PDPs give us the tools we need to put action computation, the mechanism of action, and state measurement at the same location in the network!
		\end{itemize}
		\item If addressed, what do I use them for?
		\begin{itemize}
			\item Identify the common aspects of non-NetFPGA P4-capable devices.
			\item Determine whether these allow a common architecture (but not common reimplementation since different languages, low-level specifics).
			\item Might need to describe the same mechanism as implemented in both Netronome and Barefoot?
		\end{itemize}
		\item What applications is this affecting?
		\begin{itemize}
			\item PDP applications in general.
		\end{itemize}
	\end{itemize}
\end{itemize}

@@

\newpage

>>>>

	\item Training deep RL models has its own costs (need many parallel simulations). What if we only have one stream of experience to learn from? E.g., evolution of the system is too difficult to predict and model. In general, DNNs can't be trained effectively from a single, online, real-time stream of experience.
	\begin{itemize}
		\item What can I do with these observations?
		\begin{itemize}
			\item This suggests that we should also look into non-DNN based RL approaches, if we find that RL is the best tool for the job.
		\end{itemize}
		\item What can I do to address this?
		\begin{itemize}
			\item Employ classical RL methods, which don't need many streams of parallel execution traces to learn effectively.
		\end{itemize}
		\item If addressed, what do I use them for?
		\begin{itemize}
			\item There's ongoing research which attempts to execute NN/DNN-based RL/ML models in switches, but these work under heavy concessions. Need binarisation, reduced accuracy, can't run backpropagation on SmartNIC hardware...
			\item Training and format conversion must happen off of the device, so can't be done online.
		\end{itemize}
		\item What applications is this affecting?
		\begin{itemize}
			\item In-network RL applications needing real-time evolution, where DNN online training is not doable.
			\item Likely invites some accuracy impact---linear (e.g., tile-coded) function approximation not as expressive or powerful as DNNs.
		\end{itemize}
		\item What would its solution be useful for?
		\begin{itemize}
			\item Ensures that online learning is possible in the contexts we're interested in.
			\item I.e., DDoS prevention (evolving problem).
		\end{itemize}
	\end{itemize}

	\item PDP hardware is advertised as supporting P4, EBPF... But almost all implementations compile to a more complex/expressive language. Presence of externs is almost universal when it comes to in-switch compute---i.e., Tofino Native Architecture\footnote{\url{    https://www.barefootnetworks.com/products/brief-p4-studio/}}, Netronome Micro-C\footnote{\url{https://www.netronome.com/products/datapath-programming-tools/}}, P4$\rightarrow$NetFPGA toolchain\footnote{\url{https://github.com/NetFPGA/P4-NetFPGA-public}}.
	\begin{itemize}
		\item What can I do with these observations?
		\begin{itemize}
			\item We should use P4 where possible to make implementation of in-network compute possible.
			\item \emph{But} we would be remiss not to make use of the multicore, general-purpose compute that many of these devices are fundamentally built to do.
			\item In-network compute and/or PDPs give us the tools we need to put RL action computation, the mechanism of action, and state measurement at the same location in the network!
		\end{itemize}
		\item If addressed, what do I use them for?
		\begin{itemize}
			\item Identify the common aspects of non-NetFPGA P4-capable devices.
			\item Determine whether these allow a common architecture (but not common reimplementation since different languages, low-level specifics).
			\item Might need to describe the same mechanism as implemented in both Netronome and Barefoot?
		\end{itemize}
		\item What applications is this affecting?
		\begin{itemize}
			\item PDP applications in general.
		\end{itemize}
	\end{itemize}
\end{itemize}

@@
